%
% assembly.tex
%
% Copyright The PC-104 Adapter Contributors.
%
% PC-104 Adapter Documentation
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 4.0
% International License. To view a copy of this license,
% visit http://creativecommons.org/licenses/by-sa/4.0/.
%

%
% \brief Assembly instructions chapter.
%
% \author Gabriel Mariano Marcelino <gabriel.mm8@gmail.com>
%
% \version 3.0.0
%
% \date 2020/10/19
%

\chapter{Assembly Instructions} \label{ch:assembly}

This chapter presents the assembly instructions for the version 3.0 PCB. Since the same PCB is used for both board positions, the assembly process is identical except for the selection and placement of the PC-104 connectors that define whether the board will be configured as a top or bottom board. The interconnection cables between the two assembled boards are also described.

This project does not have sensible components (electrostatic or temperature), and no major care should be taken during the solder process. A recommended temperature of the soldering iron can be 350 $^{\circ}$C or lower.

\section{PCB Fabrication}

There is no major concerns about the PCBs fabrication. The boards were not designed to be fabricated without a solder mask, but if possible a Class 3 fabrication is recommended. A list with the recommended configuration can be seen in \autoref{tab:pcb-fabrication}.

\begin{table}[!h]
    \centering
    \begin{tabular}{lc}
        \toprule[1.5pt]
        \textbf{Parameter}      & \textbf{Value} \\
        \midrule
        Size                    & 86.26 $\times$ 91.9 mm \\
        Layers                  & 4 \\
        Thickness               & 1.6 mm \\
        Minimum Hole Size       & 0.3 mm \\
        Silkscreen Color        & White \\
        Surface Finish          & HASL with lead \\
        Via Process             & Tenting vias \\
        Material                & FR-4: TG150 \\
        Minimum Track/Spacing   & 6/6 mil \\
        Solder Mask Color       & Green \\
        Gold Fingers            & No \\
        Finish Copper           & 1 oz Cu (Inner Copper: 1 oz) \\
        \bottomrule[1.5pt]
    \end{tabular}
    \caption{Recommended configuration for fabrication.}
    \label{tab:pcb-fabrication}
\end{table}

\section{Assembly}

The following instructions describe how to assemble the PCB as a top board.

\begin{enumerate}
    \item Solder the PC-104 connectors J1 and J2 (TSW-126-07-G-D) on the bottom side of the PCB.
    \item Solder the PC-104 connectors J3 and J4 (SSW-126-01-G-D) on the top side of the PCB.
\end{enumerate}

The same assembly procedure applies when configuring the PCB as a bottom board. Only the placement and orientation of the PC-104 connectors differ according to the required configuration.

\begin{enumerate}
    \item Solder the PC-104 connectors J1 and J2 (SSW-126-01-G-D) on the top side of the PCB.
    \item Solder the PC-104 connectors J3 and J4 (TSW-126-07-G-D) on the bottom side of the PCB.
\end{enumerate}

\notte{Use the ``This side up!'' marking on one side of the PCB to identify its top side! This orientation must be respected because the PCB is not symmetrical!}
